Formatting instructions for NIPS 2018

### 2018-05-02 NIPS 2018/main.tex

We define the Bellman residual of a $Q$-function $Q$ as $B(Q) \triangleq TQ - Q$. Notice that a $Q$-function $Q$ is optimal if, and only if, $B(Q)(s,a) = 0$ for all $s,a$. Furthermore, if we assume the existence of a distribution $\mu$ over $\mathcal{S}\times\mathcal{A}$, the expected Bellman error of $Q$ is defined as the expected Bellman residual of $Q$ under $\mu$. Although minimizing the empirical Bellman error would be

@@

@@

@@

>>>>

When learning the optimal value function, a quantity of interest is how close a given $Q$-function is to the fixed-point of the Bellman operator. This is given by its Bellman residual, defined by $B(Q) \triangleq TQ - Q$. Notice that $Q$ is optimal if, and only if, $B(Q)(s,a) = 0$ for all $s,a$. Furthermore, if we assume the existence of a distribution $\mu$ over $\mathcal{S}\times\mathcal{A}$, the expected squared Bellman error of $Q$ is defined as the expected squared Bellman residual of $Q$ under $\mu$, $\mathbb{E}_{\mu}\left[ B^2(Q) \right]$. Although minimizing the empirical Bellman error is an appealing objective, it is well-known that an unbiased estimator requires two independent samples of the next state $s'$ of each $s,a$ (e.g., \cite{} \todo{cite Maillard}). In practice, the empirical Bellman error is typically replaced by the TD error, which approximates the former using a single transition sample. Given a dataset of $N$ samples, the TD error is computed as $\frac{1}{N}\sum_{i=1}^N (r_i + \gamma \max_{a'} Q(s_i',a') - Q(s_i,a_i))^2$.

@@

When working with Bayesian approaches, the posterior distribution of hidden variables $\bm{w} \in \mathbb{R}^K$ given data $D$,
\begin{equation}\label{eq:bayes}
p(\bm{w} | D) = \frac{p(D | \bm{w})p(\bm{w})}{p(D)} = \frac{p(D | \bm{w})p(\bm{w})}{\int_{\bm{w}} p(D | \bm{w})p(\bm{w})},
\end{equation}
is typically intractable for many models of interest (e.g., when working with deep neural networks) due to difficulties in computing the integral of Eq. \eqref{eq:bayes}. The main intuition behind variational inference \cite{} \todo{CITE} is to approximate the intractable posterior $p(\bm{w} | D)$ with a simpler distribution $q_{\bm{\xi}}(\bm{w})$. The latter is chosen in a parametric family, with variational parameters $\bm{\xi}$, as the minimizer of the Kullback-Leibler (KL) divergence w.r.t. $p$:
\begin{equation}
\min_{\bm{\xi}} KL\left(q_{\bm{\xi}}(\bm{w})\ ||\ p(\bm{w} \mid D)\right)
\end{equation}
It is well-known that minimizing the KL divergence is equivalent to maximizing the so-called \textit{evidence lower bound} (ELBO), which is defined as:
\begin{equation}
\text{ELBO}(\bm{\xi}) = \mathbb{E}_{\bm{w} \sim q_{\bm{\xi}}}\left[ \log p(D | \bm{w}) \right] - KL\left(q_{\bm{\xi}}(\bm{w})\ ||\ p(\bm{w})\right)
\end{equation}
Intuitively, the best approximation is the one that maximizes the expected log-likelihood of the data, while minimizing the KL divergenge w.r.t. the prior $p(\bm{w})$.

@@

\section{Theoretical Analysis}

@@

\section{Proofs of Theorems}
